\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-8pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item[]\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemGen}[1]{
  \item\small{
    #1 \vspace{-2pt}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item[]
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      {\small#3} & {\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingShort}[2]{
  \vspace{-1pt}\item[]
    \begin{tabular*}{1\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0mm]}
%\newcommand{\resumeSubHeadingListStart}{}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
%\newcommand{\resumeSubHeadingListEnd}{}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Rakesh Singh}} & Email: \href{mailto:rakesh.singh@tum.de}{rakesh.singh@tum.de}\\
  \href{https://www.linkedin.com/in/genzing/}{https://www.linkedin.com/in/genzing/} & Mobile: +4917661015323 \\
\end{tabular*}


%-----------EDUCATION-----------------
\vspace{-1pt}
\section{Education}
  \vspace{-3.2pt}
  %\resumeSubHeadingListStart
    \resumeSubheading
      {Technical University of Munich}{Apr. 2016 -- Feb. 2019}
      {Master of Science in Computer Science}{ Munich, Germany}\\
      \vspace{5pt}
      \small{{\textbf{Master Thesis:} Designing a Mobile Identification and User-Profile Solution for an Urban IoT Network.}}\newline
      \small{{\textbf{Major:} Distributed Systems and \textbf{Minor:} High Performance Computing}}
    \resumeSubheading
      {National Institute of Technology, Durgapur}{Aug. 2007 -- May. 2011}
      {Bachelor of Technology in Information Technology}{WB, India}\\
      \vspace{5pt}
      \small{{Coursework heavily focused on Software Engineering Principles, Algorithms and Data Structures and Computer Networks.}}
  %\resumeSubHeadingListEnd
\vspace{-2pt}

%-----------EXPERIENCE-----------------
\section{Work Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Goldman Sachs}{Oct 2013 - Mar 2016}
      {Senior Software Developer (C++, Python) }{ Bengaluru, IN }
      \resumeItemListStart
        \resumeItem{Algorithmic Trading}
          {Involved in Designing and Implementation of Trading Algorithms like Iceberg in C++. Responsible for Order Management, Exchange Connectivity and Smart Order Routing.}
        \resumeItem{Stock Connect}
          {Played a Pivotal role in establishing exchange connectivity between HongKong and Shanghai.}
        \resumeItem{System Migration}
          {Involved in the migration of systems from bare metal hosts to Virtual Machines, thus increasing the scalability and robustness of the systems. }
      \resumeItemListEnd
    \resumeSubheading   
    {Misys}{Jul 2011 - Sep 2013}
      {Software Engineer (C++0x/11, MySQL)}{ Bengaluru, India}
      \resumeItemListStart
        \resumeItem{LoanIQ}
          {Syndicated Loan Management Software. Involved in core features like EOD batch jobs and Accruals calculations. Optimized and fixed bugs to speedup batch processing by 40\%.}
    \resumeItemListEnd
  \resumeSubHeadingListEnd
  
  %-----------Internships and Working Students-----------------
\section{Internships}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Technical University of Munich}{Apr, 2018 - Present}
      {Graduate Teaching Assistant }{Munich, Germany}
      \resumeItemListStart
        \resumeItem{Tutor}
          {Responsible for programming sessions of Parallel Programming Course consisting of Masters students  and Teaching C programming to Bachelor students.}
      \resumeItemListEnd
    \resumeSubheading   
    {Digital Product School}{Jan 2018 - Mar 2018}
      {Software Engineer (React, C, Python)}{Munich, Germany}
      \resumeItemListStart
        \resumeItem{Kubi}
          {User Research, Implementation, Testing of an Interactive console for people suffering from Dementia. }
     \resumeItemListEnd
     
     \resumeSubheading   
    {Allianz Technologies(AMOS)}{Oct 2016 - Sep 2017}
      {IT Consulting and PMO}{Munich, Germany}
      \resumeItemListStart
        \resumeItem{Data Center Consolidation}
          {Involved in Microsoft Exchange Migration of 80000 mailboxes and Developed a process to decommission inactive mailboxes resulting in cost savings by 30\% across EMEA Business Units. }
     \resumeItemListEnd
     
     \resumeSubheading   
        {Pure Flavours}{Aug 2016 - Sep 2016}
        {Software Developer (Magento, PHP)}{Munich, Germany}
      \resumeItemListStart
       \resumeItem{E-commerce}
          {Developed tax categorization for different B2B customers and fixed bugs related to tax calculations. }
     \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
     \resumeSubheadingShort
      {[X]Team UnternehmerTUM \textnormal{}}{Jan 2018 - Jan 2019}
    \resumeItemListStart
      \resumeItemGen{Assisted in Industry prototyping projects for \textbf {Peri, Wacker, TetraPak and Siemens} to support digital innovation using latest technologies and Agile Methodologies like Kanban and Scrum. }
      \resumeItemGen{Gained expertise in hardware and software prototyping by using various kinds of sensors/micro-controllers. }
    \resumeItemListEnd
    
     \resumeSubheadingShort
      {Mobile Vision \textnormal{(Android(Java))}}{Sep 2017 - Mar 2018}
      \resumeItemListStart
        \resumeItemGen{An Android app developed as a part of the lab course to read speed signs and generate warning for the over speeding driver using mobile camera. Used OpenCV, OCR and YOLO algorithms.}
        \resumeItemListEnd
  
   \resumeSubheadingShort
      {Parallelisation of Linear Acoustic Equation Solver \textnormal{(C++, Unix)}}{Dec 2016 -- Jan 2017}
      \resumeItemListStart
        \resumeItemGen{Implemented multithreaded applications for heat wave simulations and abalone game using MPI, OpenMP.}
        \resumeItemGen {Optimized the provided code by using techniques like Data dependency analysis, Cache Optimization techniques.}
        \resumeItemListEnd

  \resumeSubHeadingListEnd

 %--------Programming Skills------------    
\section{Programming Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Languages}
      { C/C++11/14, QT, Python, Java \hfill \textbf{Web \& Database:} PHP, HTML, NodeJS, MySQL, Oracle}
    \resumeSubItem{Technologies}
    { Docker, Kubernetes, GIT, Kafka, Microsoft Azure, Sketch, Tableau}
  \resumeSubHeadingListEnd


%--------Awards and Honours------------
\section{Awards and Honours}
 % \resumeSubHeadingListStart
      \small\textbf{1st Prize}{ Winner of FC Bayern International Hackathon as a part of Team Adidas.}\break
      \small\textbf{1st Prize}{ in TUM Think Make Start for the most innovative solution resulting in a start up named SolosMirrors.}
 % \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}


